Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-27 paper/ijcai16.tex
paper: update to the final (?) figures.

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3 loss} & {\sc synthetic 4 loss} & {\sc synthetic 5 loss} & {\sc synthetic 5 time}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:comparison} {\sc SetMargin} vs Guo vs Viappiani.}
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{2}{c}{{\sc per query loss}} &
        \multicolumn{2}{c}{{\sc per iter. loss}}
        \\
        {\sc synthetic 4} & {\sc synthetic 6} & {\sc synthetic 4} & {\sc synthetic 6}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/loss}
        \\
        \hline
    \end{tabular}
    \caption{\label{fig:selfcomparison} Self-comparison experiment. Only
    losses, per-query and per-iteration. Runtime described in the text. Each
    row is a user sampling mode. Three curves per plot: $k=2$ vs $k=3$ vs
    $k=4$.}
    }
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{4}{c}{{\sc uniform sparse}}
        \\
        \multicolumn{2}{c}{{\sc loss/time per iteration}} &
        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc normal sparse}}
        \\
        \multicolumn{2}{c}{{\sc loss/time per iteration}} &
        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time} &
        \includegraphics[width=10em]{figures/loss} &
        \includegraphics[width=10em]{figures/time}
        \\
        \hline
    \end{tabular}
    }
    \caption{Results for the PC dataset.}
\end{figure}

>>>>

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3 loss} & {\sc synthetic 3 time} & {\sc synthetic 4 loss} & {\sc synthetic 4 time}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_uniform_sparse_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_3_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_others_4_normal_sparse_per_iter_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:comparison} Comparison between {\sc SetMargin} and the
    Bayesian competitors.}
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{2}{c}{{\sc loss per iter.}} &
        \multicolumn{2}{c}{{\sc loss per query}}
        \\
        {\sc synthetic 4} & {\sc synthetic 5} & {\sc synthetic 4} & {\sc synthetic 5}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_uniform_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_uniform_per_query_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc normal sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_4_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_vs_self_5_normal_sparse_per_query_loss}
        \\
        \hline
     \end{tabular}
    }
    \caption{\label{fig:selfcomparison} Comparison for {\sc SetMargin} with
    $k=2,3,4$.}
\end{figure}

% times for the figure above
% synthetic_vs_self_4_normal_sparse_per_iter_time
% synthetic_vs_self_4_normal_sparse_per_query_time
% synthetic_vs_self_4_uniform_per_iter_time
% synthetic_vs_self_4_uniform_per_query_time
% synthetic_vs_self_5_normal_sparse_per_iter_time
% synthetic_vs_self_5_normal_sparse_per_query_time
% synthetic_vs_self_5_uniform_per_iter_time
% synthetic_vs_self_5_uniform_per_query_time

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{2}{c}{{\sc loss/time per iter.}} &
        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
        \multicolumn{4}{c}{{\sc uniform sparse}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc normal sparse}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:pc} Results for {\sc SetMargin} on the constructive PC
    dataset.}
\end{figure}
